\begin{minipage}[t]{\sw}
\slidenumber
\LARGE
{\bf Static Properties of Variables}\exx
\Large
A {\em variable} in a program is a symbol
that has an associated value at run-time.
One of the principal issues in determining the behavior of a program
is determining {\em how} to find the value of a variable at run-time.
At any instance in time, the value associated with a variable
is called a {\em binding} of the variable to the value.\exx
An {\em expression} is a language construct that has a value at run-time.
A variable, by itself, is therefore an expression,
but other language constructs can also have values:
for example \verb'x+y' is an expression
if \verb'x' and \verb'y' are numeric-valued variables.\exx
A programming language that is designed solely for the purpose
of evaluating expressions is called an {\em expression-based language}.
Many of the languages we construct in these notes are expression-based,
especially early on.
\verb'Scheme', \verb'ML', and \verb'Haskell' are examples
of expression-based languages used in practice.
Expression-based languages do their looping principally using recursion.\exx
A programming language whose language constructs are designed
to ``do something''
(such as assigning the value of an expression to a variable
or displaying the value of an expression to standard output)
is called an {\em imperative language}.
In an imperative language, a language construct
that ``does somthing'' is called a {\em statement};
Imperative languages are therefore often called {\em statement-based}.
\verb'C', \verb'Java', and \verb'Python' are examples
of imperative languages used in practice.
Imperative languages do their looping principally using a form of ``goto''.\exx
Expression-based languages get their power
from defining and applying {\em functions},
so another term describing such languages is {\em functional}.
\end{minipage}
\clearpage
