\begin{minipage}[t]{\sw}
\slidenumber
\LARGE
{\bf Language TYPE0} (continued)\exx
\Large
Our \verb'TYPE0' language has two new expressions:
a \verb'TrueExp' and a \verb'FalseExp',
with obvious concrete and abstract syntax:\exx
\emm\begin{tabular}{ll}
\verb'<exp>:TrueExp' & \verb'::= TRUE'\\
    & \VerbBox{\fbox}{\verb'TrueExp()'} \\
\verb'<exp>:FalseExp' & \verb'::= FALSE'\\
    & \VerbBox{\fbox}{\verb'FalseExp()'} \\
\end{tabular}\exx
What should the \verb'eval' method return for these classes?
So far, we have used an \verb'IntVal' of zero to be false
and everything else to be true.
Once we have syntax for \verb'true' and \verb'false' expressions,
we should introduce corresponding semantics.
We therefore create a new \verb'Val' type, \verb'BoolVal',
that represent the values of these expressions.
The code for the \verb'BoolVal' class is in the \verb'val' file.\exx
Once we have a \verb'BoolVal',
we can define the \verb'eval' behavior
for the \verb'TrueExp' and \verb'FalseExp' classes.
Here's the code for \verb'TrueExp' --
the code for \verb'FalseExp' is nearly identical:
\begin{qv}
public Val eval(Env env) {
    return new BoolVal(true);
}
\end{qv}
Obviously the \verb'isTrue' method applied
to a \verb'BoolVal' object constructed with \verb'true'
should return true, and similarly a \verb'BoolVal' object
constructed with \verb'false' should return false.
The \verb'isTrue' method applied to any other value
(either an \verb'IntVal' or a \verb'ProcVal')
should throw an exception.
\end{minipage}
